### 2020-08-24 paper/main.tex
Move from article to report

\documentclass{article}
\usepackage{import}

@@

\section*{Definitions}
\input{definitions.tex}

\section{Perfect Graphs}

@@

\subsection{Strong Perfect Graph Theorem}

@@

\section{Recognizing Berge Graphs}

@@

\subsection{Recognition algorithm Overview}

@@

\subsubsection{Simple structures}
\label{SimpleStructures}

\paragraph{Pyramids}

@@

\subparagraph{Finding Pyramids}

@@

\paragraph{Jewels}

@@

\paragraph{Configurations of type $\T_1$}

A configuration of type $\T_1$ is a hole of length 5. To find it we simply iterate all choices of paths of length of 4, and check if there exists a fifth vertex to complete the hole. See paragraph \ref{Optimizations} for more implementation details.

\paragraph{Configurations of type $\T_2$}

@@

\paragraph{Configurations of type $\T_3$}

@@

We will skip the proof that each graph containing $\T_3$ is not Berge. See paragraph 6.7 of \cite{MC05} for the proof.

\subsubsection{Amenable holes.}
\label{AmenableHoles}

@@

\subsection{Implementation}

@@

\subsubsection{Optimizations}\label{Optimizations}
Bottlenecks in performance (next path, are vectors distinct etc).\\
\TODO{In our graph preprocessing we have a pointer to next edge in order to speed up generating next path.}
\TODO{We used callgrind to get idea of methods crucial for time.}
\TODO{In general enumerating all paths is crucial. As is checking if vector has distinct values.}
\TODO{Jewels -- we iterate all possibly chordal paths and check if they are ok - much faster}
\TODO{$\T_1$ -- we iterate all paths of length 4 and check if there exists a fifth vertex to complete the hole - much faster than iterating vertices.}

@@

\subsection{Parallelism with CUDA (?)}

@@

\subsection{Experiments}

@@

\section{Coloring Berge Graphs}

\subsection{Ellipsoid method}

@@

\subsection{Combinatorial Method}

@@

\section{Perfect Graph Coloring algorithm}
TODO

>>>>

\documentclass{report}
\usepackage{import}

@@

\chapter*{Definitions}
\input{definitions.tex}

\chapter{Perfect Graphs}

@@

\section{Strong Perfect Graph Theorem}

@@

\chapter{Recognizing Berge Graphs}

@@

\section{Recognition algorithm Overview}

@@

\subsection{Simple structures}
\label{SimpleStructures}

\subsubsection{Pyramids}

@@

\paragraph{Finding Pyramids}

@@

\subsubsection{Jewels}

@@

\subsubsection{Configurations of type $\T_1$}

A configuration of type $\T_1$ is a hole of length 5. To find it we simply iterate all choices of paths of length of 4, and check if there exists a fifth vertex to complete the hole. See \cref{Optimizations} for more implementation details.

\subsubsection{Configurations of type $\T_2$}

@@

\subsubsection{Configurations of type $\T_3$}

@@

We will skip the proof that each graph containing $\T_3$ is not Berge. See section 6.7 of \cite{MC05} for the proof.

\subsection{Amenable holes.}
\label{AmenableHoles}

@@

\section{Implementation}

@@

\subsection{Optimizations}\label{Optimizations}
Bottlenecks in performance (next path, are vectors distinct etc).\\
\TODO{In our graph preprocessing we have a pointer to next edge in order to speed up generating next path.}
\TODO{We used callgrind to get idea of methods crucial for time.}
\TODO{In general enumerating all paths is crucial. As is checking if vector has distinct values.}
\TODO{Jewels -- we iterate all possibly chordal paths and check if they are ok - much faster}
\TODO{$\T_1$ -- we iterate all paths of length 4 and check if there exists a fifth vertex to complete the hole - much faster than iterating vertices.}

@@

\section{Parallelism with CUDA (?)}

@@

\section{Experiments}

@@

\chapter{Coloring Berge Graphs}

\section{Ellipsoid method}

@@

\section{Combinatorial Method}

@@

\chapter{Perfect Graph Coloring algorithm}
TODO
